---
title: "DACSS 690V Deliverables"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

## Intro {.sidebar}

Preparing the dashboard based on the instructions given at 
@magallanes_reyes_data_2022, and @aden-buie_flexdashboard_2023. 

You can find the code for this dashboard here:
https://github.com/ACC-UMASS/FinalProject-690V

DACSS 690V Deliverable Dashboard

## column {.tabset. tabset.fade}

### Univariate Categorical Plot

```{r}
readRDS("liberalization2020PercentFinal.RDS")
```


### Univariate Numerical Plot

```{r}
readRDS("crimeRate2020New.RDS") 
```


### Bivariate Plot


```{r}
readRDS("bivariatePlotFinal.RDS")
```


### Choropleth Map

```{r}
readRDS("mapFinal.RDS")
```


### References:
I created the cannabisData2020 dataset that was utilized for these plots. The data was collected from the following sources:
FBI Uniform Crime Reporting program
The FBI Crime Data Explorer 
The United States Department of Justice 
The Drug Enforcement Administration
Each state’s government website
The Federal Bureau of Prisons
